Observing and Predicting Knowledge Worker Stress, Focus and Awakeness in the Wild

### 2020-10-20 IJHCSSubmission/bp_results_1.tex
fixed typo

\begin{table}
  \centering
      \includegraphics[width=0.8\textwidth]{distributiontable.pdf}
  \caption{The distribution of the responses of each participant to the three questions asked during the day are shown. Each bar in the histograms represent one of the \ref{five} values on the 5-point Likert scale we asked participants to respond with, where the far left side of the histograms are 1/Not at all, and the far right sides are 5/Extremely}
   \label{responseDistribution}
   %\vspace*{-2mm}
\end{table}

>>>>

\begin{table}
  \centering
      \includegraphics[width=0.8\textwidth]{distributiontable.pdf}
  \caption{The distribution of the responses of each participant to the three questions asked during the day are shown. Each bar in the histograms represent one of the five values on the 5-point Likert scale we asked participants to respond with, where the far left side of the histograms are 1/Not at all, and the far right sides are 5/Extremely}
   \label{responseDistribution}
   %\vspace*{-2mm}
\end{table}
